Design and Implementation of Probabilistic Programming Language Anglican

### 2016-11-27 paper/paper.tex
update

\section{Summary}
\label{seq:summary}

In this paper, we presented design and implementation internals
of the \emph{probabilistic programming system} Anglican. Implementing
a language is an interesting endeavour, in particular when the
language implements a new paradigm, in this case probabilistic
programming. Functional programming is a natural complement of
probabilistic programming --- the latter allows both concise and
expressive specification of probabilistic generative models and
efficient implementation of inference algorithm.

Implementing a probabilistic language on top and in tight
integration with a functional language, Clojure, both helped
us to accomplish an ambitious goal in a short time span, and
provided important insights on structure and semantics of
probabilistic concepts incorporated in Anglican. Computational
efficiency and expressive power of Anglican owe to adherence to
the functional approach as much as to rich inference
opportunities of the Anglican environment.

>>>>

\section{Conclusion}
\label{seq:summary}

In this paper, we presented design and implementation internals
of the \emph{probabilistic programming system} Anglican. Implementing
a language is an interesting endeavour, in particular when the
language implements a new paradigm, in this case probabilistic
programming. Functional programming is a natural complement of
probabilistic programming --- the latter allows both concise and
expressive specification of probabilistic generative models and
efficient implementation of inference algorithms.

Implementing a probabilistic language on top of and in tight
integration with a functional language, Clojure, both helped
us to accomplish an ambitious goal in a short time span, and
provided important insights on structure and semantics of
probabilistic concepts incorporated in Anglican. Computational
efficiency and expressive power of Anglican owe to adherence to
the functional approach as much as to rich inference
opportunities of the Anglican environment.
